COVID Shutdown Regulations Negatively Impact Employment and Sales of Restaurants in Ontario

### 2021-02-26 outputs/paper/paper.Rmd
Edit graphs

header-includes:
  \usepackage{float}
  \floatplacement{figure}{H}

@@

&nbsp; &nbsp; We organize he rest of paper as follows: In Data section, we first discuss interventions of the experiment. Next, we introduce sampling methods and survey methodologies to collect the data. And then, we discuss main findings from survey results. In Discussion section, we would elaborate on concerns about the intervention on city selections, sampling methods and survey methodologies. And we also propose our thoughts on further policy implications. In Appendix, we include screenshots of survey contents.^[ Code and data are available at the GitHub repo: https://github.com/honn-ishinn/restaurants_covid_shutdown"]

@@

```{r question3, fig.align='center', fig.cap="Layoff Situation due to COVID 19", fig.width=6, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
data.frame(table(simulated_dataset$q3_layoff,simulated_dataset$q1_city))%>%
  ggplot(aes(Var1, Freq,fill=Var2)) +
  theme_minimal()+
    geom_bar(stat = "identity",position = position_dodge(), width = 0.7)+
   theme(plot.title = element_text(hjust = 0.5)) +
  ylab("Number of Responses")+
  xlab("Number of Laid-offs")+
  ggtitle("Layoff Situation due to COVID 19")+
  guides(fill=guide_legend(title="City"))

@@

```
The following figure (\@ref(fig:q8)) demonstrates restaurant owners' opinions towards the expected survivability of their businesses. It is very unfortunate that restaurants in Brantford are not as positive to continue their businesses for longer times, indicating a stressful operating situation during these continuing shutdown period. While on the other hand, restaurants in Peterborough generally expect to survive longer, showing stronger confidence to continue their businesses after reopening.
```{r q8, fig.align='center', fig.cap="Expected Survival Time if Current Situation Continues", fig.width=6, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
# Use

data.frame(table(simulated_dataset$q8_survive,simulated_dataset$q1_city))%>%
    mutate(Var1 = fct_relevel(Var1 ,"Unknown","Longer than 6 months","3 to 6 months","Less than 3 months")) %>% 
  ggplot(aes(Var1, Freq,fill=Var2)) +
  theme_minimal()+
  geom_bar(stat = "identity",width = 0.8, position = position_dodge()) +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab("Number of Responses")+
  xlab("Expected Survival Time")+
  ggtitle("Expected Survival Time if Current Situation Continues")+
  guides(fill=guide_legend(title="City"))+
  coord_flip()
```

@@

```{r}
simulated_dataset %>%
  tabyl(q1_city, q11_rate_support)%>%
  adorn_totals("row")%>%
  adorn_totals("col")%>%
  adorn_percentages("row")%>%
  adorn_pct_formatting(digits=2)%>%
  adorn_ns()%>%
  adorn_title("combined",row_name = "City", col_name = "Rating")%>%
  kable("html", align = 'ccccccc', caption = 'Number or percentage of each rating level')%>%
  kable_styling(full_width = F)
```

 As an agent to gather relevant feedback to the Ontario Government, we asked restaurants how they found the governmental support programs so far. According to Table, both cities stated the effectiveness of the governmental support programs, nevertheless, this figure also implies to their satisfaction and also appreciation for these programs by business entities in both cities.
```{r}
# use
data.frame(table(simulated_dataset$q13_CEWS,simulated_dataset$q1_city))%>%
#  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
  ggplot(aes(Var1, Freq,fill=Var2)) +
    geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
  ylab("Number of responses")+
  xlab("Options")+
  ggtitle("Restaurants receiving the Canada Emergency Wage Subsidy(CEWS)")+
  guides(fill=guide_legend(title="City"))+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 0))+
  coord_flip()
```

According to figure 14, Peterborough restaurants are using more Canadian Emergency Wage Subsidy (CEWS)- a governmental program available for businesses to reimburse a considerable portion of their employees’ salaries – compared to Brantford restaurants. It is reasonable for Brantford restaurants to have utilized less of this grant because CEWS covers the wages partially and yet, the employer should pay the rest of the employee’s salary. This is also consistent with the results in figure 3 where they indicated to have had more layoffs.

>>>>

header-includes:
 - \usepackage{float}
 - \floatplacement{figure}{H}
 - \floatplacement{table}{H}

always_allow_html: yes

@@

&nbsp; &nbsp; We organize the rest of paper as follows: In Data section, we first discuss interventions of the experiment. Next, we introduce sampling methods and survey methodologies to collect the data. And then, we discuss main findings from survey results. In Discussion section, we would elaborate on concerns about the intervention on city selections, sampling methods and survey methodologies. And we also propose our thoughts on further policy implications. In Appendix, we include screenshots of survey contents.^[ Code and data are available at the GitHub repo: https://github.com/honn-ishinn/restaurants_covid_shutdown"]

@@

```{r question3, fig.align='center', fig.cap="Layoff Situation due to COVID 19", fig.width=7, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
data.frame(table(simulated_dataset$q3_layoff,simulated_dataset$q1_city))%>%
  ggplot(aes(Var1, Freq,fill=Var2)) +
  theme_minimal()+
    geom_bar(stat = "identity",position = position_dodge(), width = 0.7)+
   theme(plot.title = element_text(hjust = 0.5)) +
  ylab("Number of Responses")+
  xlab("Number of Laid-offs")+
  ggtitle("Layoff Situation due to COVID 19")+
  guides(fill=guide_legend(title="City"))

@@

```{r q8, fig.align='center', fig.cap="Expected Survival Time if Current Situation Continues", fig.width=6, fig.height=3, echo= FALSE, message=FALSE, warning=FALSE}
# Use

data.frame(table(simulated_dataset$q8_survive,simulated_dataset$q1_city))%>%
    mutate(Var1 = fct_relevel(Var1 ,"Unknown","Longer than 6 months","3 to 6 months","Less than 3 months")) %>% 
  ggplot(aes(Var1, Freq,fill=Var2)) +
  theme_minimal()+
  geom_bar(stat = "identity",width = 0.8, position = position_dodge()) +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab("Number of Responses")+
  xlab("Expected Survival Time")+
  ggtitle("Expected Survival Time if Current Situation Continues")+
  guides(fill=guide_legend(title="City"))+
  coord_flip()
```
The figure (\@ref(fig:q8)) shown above demonstrates restaurant owners' opinions towards the expected survivability of their businesses. It is very unfortunate that restaurants in Brantford are not as positive to continue their businesses for longer times, indicating a stressful operating situation during these continuing shutdown period. While on the other hand, restaurants in Peterborough generally expect to survive longer, showing stronger confidence to continue their businesses after reopening.

@@

```{r q11,echo=FALSE }
t1<-simulated_dataset %>%
  tabyl(q1_city, q11_rate_support)%>%
  adorn_totals("row")%>%
  adorn_totals("col")%>%
  adorn_percentages("row")%>%
  adorn_pct_formatting(digits=2)%>%
  adorn_ns()%>%
  adorn_title("combined",row_name = "City", col_name = "Rating")

kable(t1, caption = 'Number or percentage of each rating level')%>%
  kable_styling(full_width = F)

 As an agent to gather relevant feedback to the Ontario Government, we asked restaurants how they found the governmental support programs so far. According to Table, both cities stated the effectiveness of the governmental support programs, nevertheless, this figure (Table \@ref(tab:q11)) also implies to their satisfaction and also appreciation for these programs by business entities in both cities.
```{r q14, fig.align='center', fig.cap="Restaurants receiving the Canada Emergency Wage Subsidy(CEWS)", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}

data.frame(table(simulated_dataset$q13_CEWS,simulated_dataset$q1_city))%>%
  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","I do not know","No","Yes"))%>%
  ggplot(aes(Var1, Freq,fill=Var2)) +
    geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
  ylab("Number of responses")+
  xlab("Options")+
  ggtitle("Restaurants receiving the Canada Emergency Wage Subsidy(CEWS)")+
  guides(fill=guide_legend(title="City"))+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 0))+
  coord_flip()
```

According to Figure \@ref(fig:q14), Peterborough restaurants are using more Canadian Emergency Wage Subsidy (CEWS)- a governmental program available for businesses to reimburse a considerable portion of their employees’ salaries – compared to Brantford restaurants. It is reasonable for Brantford restaurants to have utilized less of this grant because CEWS covers the wages partially and yet, the employer should pay the rest of the employee’s salary. This is also consistent with the results in figure 3 where they indicated to have had more layoffs.

```{r q15, fig.align='center', fig.cap="How much loans have you applied for the COVID-19 related reasons?", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
data.frame(table(simulated_dataset$q14_loans,simulated_dataset$q1_city))%>%
  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
  ggplot(aes(Var1, Freq,fill=Var2)) +
  geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
  ylab("Number of responses")+
  xlab("Grant value")+
  ggtitle("How much loans have you applied for the COVID-19 related reasons?")+
  guides(fill=guide_legend(title="City"))+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 0))+
  coord_flip()

```
As shown in Figure \@ref(fig:q15), Peterborough restaurants have received more business loans than restaurants in Brantford. Since loans have to be paid back, businesses operating at low operating expectation are less likely to apply for the loans. And this corresponds with our previous findings of the expected survival time (Figure \@ref(fig:q8)) and expected recovery time (Figure \@ref(fig:q10)) as mentioned before.

**They probably see a brighter future for their business to think out their repayments accordingly. However, Brantford restaurants which according to figure 8 are less hopeful to their business in future, probably mutter “It is never too late to mend” and refrain adding to their liabilities, though the loan’s interest be very low.**
